Advanced Normalization Tools (ANTS)

### 2009-07-14 Documentation/Tex/ants.tex
update refs
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@58 fd2da0a4-d968-48df-9cb5-d8c496287cbf

>>>>

\section{Annotated Bibliography}
The original statement of the symmetric normalization and template
construction methodology was given in \cite{Avants2004}.  A follow up
study that used landmark guidance to compare the chimpanzee cortex to
the human cortex was published here \cite{Avants2006} -- this study
used {\em in vivo} MRI and template-based normalization to confirm
volumetric numbers derived from an early 20th century post-mortem
study comparing one human and one chimp.  This conference article has
some additional detail and alternative updates to the methodology, in
particular application to shape-based interpolation
\cite{Avants2005b}.  Network based studies were performed here
\cite{duda08miccai,duda08cvpr}.  The main SyN paper is here
\cite{Avants2008}.  Applications to neurodegeration are here
\cite{Avants2005,Avants2008a,Grossman2008,Avants2009,Das2009,Yushkevich2009,Massimo2009}.
Hippocampus focused work is here \cite{Pluta2009,Yushkevich2009}.  The
main evaluation papers include \cite{Avants2008} and \cite{Klein2009}
for the cortex and deep brain structures whereas \cite{Pluta2009}
evaluates the use of automated and semi-automated normalization for
high-throughput hippocampus morphometry.  An additional evaluation
paper is being developed.
